Deciphering the Trends: A Comprehensive Analysis of US Birth Rates and Educational Attainment from 1980 to 2020

### 2024-02-08 outputs/paper/paper.qmd
changes to readme and introduction, adding my name

---
title: "Deciphering the Trends: A Comprehensive Analysis of US Birth Rates and Educational Attainment from 1980 to 2020"
author: "Jagpreet Singh & Alexander Guarasci"
date: "`r format(Sys.Date(), '%B %d, %Y')`" # This will add the current date
date-format: long
bibliography: references.bib
execute:
  echo: false
format: pdf
fig-pos: "H"
abstract: |
 This paper examines the trends in birth rates across the United States from 1980 to 2020, analyzing how factors like marital status, education level, and age group influence fertility decisions.
 Through the examination of comprehensive data, provided by American Economics Association [@citewebsite], we uncovered a significant decline in birth rates post-2007, with marked variations across different demographic groups, indicating a shift towards later-life parenthood and a nuanced relationship between education and fertility. These findings highlight the complex interplay between socioeconomic factors and reproductive choices, shedding light on how societal norms and individual priorities are reshaping family formation patterns.
---

@@

This paper analyses the changing landscape of birth rates in the United States over forty years, focusing on its interrelationships among age, education level, and marital status. Using extensive data from the American Economics Association, we employ rigorous statistical analysis to uncover the nuances of these trends. Our findings estimated the pronounced impact of educational attainment and marital status on fertility decisions, particularly highlighting the shift towards later-life parenthood and the evolving dynamics of family formation. Against the backdrop of significant societal transformations, we observe how these demographic factors have shaped fertility patterns.

>>>>

---
title: "Deciphering the Trends: A Comprehensive Analysis of US Birth Rates and Educational Attainment from 1980 to 2020"
author: "Jagpreet Singh, Alexander Guarasci & Jacob Gilbert"
date: "`r format(Sys.Date(), '%B %d, %Y')`" # This will add the current date
date-format: long
bibliography: references.bib
execute:
  echo: false
format: pdf
fig-pos: "H"
abstract: |
 This paper examines the trends in birth rates across the United States from 1980 to 2020, analyzing how factors like marital status, education level, and age group influence fertility decisions.
 Through the examination of comprehensive data, provided by American Economics Association [@citewebsite], we uncovered a significant decline in birth rates post-2007, with marked variations across different demographic groups, indicating a shift towards later-life parenthood and a nuanced relationship between education and fertility. These findings highlight the complex interplay between socioeconomic factors and reproductive choices, shedding light on how societal norms and individual priorities are reshaping family formation patterns.
---

@@

This paper analyses the changing landscape of birth rates in the United States over forty years, focusing on its interrelationships among age, education level, and marital status. Using extensive data from the American Economics Association, we employ rigorous statistical analysis to uncover the nuances of these trends. Our findings estimated the impact of  socioeconomic traits, such as education level and marital status, on fertility decisions to explain decrease in fertility seen over time.Particularly highlighting the shift towards later-life parenthood and the changing dynamics of family formation when it comes to marriage. The analysis shows how changes in these demographic factors have shaped fertility patterns.
